# Dyadic level synchrony analysis
```{r}
library(ggplot2)
library(readxl)
library(lme4)
library(dunn.test)
library(crqa)
library(lmerTest)
library(ARTool)
library(tidyr)
library(dplyr)
library(tidyverse)
library(ggpubr)
library(rstatix)
library(sjPlot)
```
## Mutual gaze
```{r}
df_g <- read_excel("../data/df_dyadic_gaze.xlsx")
df_g$condition <- factor(as.character(df_g$condition), levels = c("240p", "480p", "1080p"))
df_g$cq_level <- factor(as.character(df_g$cq_level), levels = c("Bad", "Poor", "Fair", "Good", "Excellent"))
df_g$dyadic <- factor(as.character(df_g$dyadic))
head(df_g)
```
### Statistics
```{r}
# Summary statistics
df_g %>%
  group_by(condition) %>%
  get_summary_stats(n_mutual_gaze, type = "common")

df_g %>%
  group_by(cq_level) %>%
  get_summary_stats(n_mutual_gaze, type = "common")

df_g %>%
  group_by(condition) %>%
  get_summary_stats(t_mutual_gaze, type = "common")

df_g %>%
  group_by(cq_level) %>%
  get_summary_stats(t_mutual_gaze, type = "common")

# Basic plot
#pdf(file = "../results/plots/mutual_time_box.pdf",  
#    width = 4, 
#    height = 4)
#ggboxplot(df_g, x = "condition", y = "t_mutual_gaze", add = "jitter", fill = "condition", xlab = "Video resolution", ylab = "Time (s)", outlier.shape = NA, width = 0.5, ylim = c(0,75), palette = "npg")
#dev.off()

# Basic plot
#pdf(file = "plots/mutual_number_box.pdf", width = 4, height = 4)
#ggboxplot(df_g, x = "condition", y = "n_mutual_gaze", add = "jitter", fill = "condition", xlab = "Video resolution", ylab = "Number", outlier.shape = NA, width = 0.5, ylim = c(0,50), palette = "npg")
#dev.off()
```
### Correlation
```{r}
# Correlation check
# Perform the correlation test
result <- cor.test(df_g$t_mutual_gaze, df_g$n_mutual_gaze)
print(result)

# 
result <- cor.test(df_g$t_mutual_gaze, df_g$d_mutual_gaze)
print(result)

#
result <- cor.test(df_g$n_mutual_gaze, df_g$d_mutual_gaze)
print(result)
```

### Mixed effect model
```{r}
# Fit the model
m.gn <- lmer(n_mutual_gaze ~ cq*condition + (1 | dyadic), data=df_g)
summary(m.gn) # sig
performance::icc(m.gn)
m.gn %>% anova()
#sjPlot::plot_model(m.gn, type = "pred", terms = c("cq", "condition"))
#sjPlot::tab_model(m.gn)

# Fit the model
m.gt <- lmer(t_mutual_gaze ~ cq*condition + (1 | dyadic), data=df_g)
summary(m.gt) # sig
performance::icc(m.gt)
m.gt %>% anova()
#sjPlot::plot_model(m.gt, type = "pred", terms = c("cq", "condition"))

# Fit the model
m.gd <- lmer(d_mutual_gaze ~ cq*condition + (1 | dyadic), data=df_g)
summary(m.gd) # no sig
performance::icc(m.gd)
m.gd %>% anova()
#sjPlot::plot_model(m.gd, type = "pred", terms = c("cq", "condition"))
#sjPlot::tab_model(m.gd)

sjPlot::tab_model(m.gt, m.gn, m.gd)
tab_model(m.gt, m.gn, m.gd, file="../results/model/m_mutual_gaze.html")
```
## Body movement coordination
```{r}
df <- read_excel("../data/df_dyadic_bm.xlsx")
df$condition <- factor(as.character(df$condition), levels = c("240p", "480p", "1080p"))
df$cq_level <- factor(as.character(df$cq_level), levels = c("Bad", "Poor", "Fair", "Good", "Excellent"))
df$dyadic <- factor(as.character(df$dyadic))
head(df)
```
### The influence of mutual gaze
```{r}
# Fit the model
m.lz.ng <- lmer(lag_zero ~ n_mutual_gaze + (1 | dyadic), data=df)
m.ps.ng <- lmer(peak_synchrony ~ n_mutual_gaze + (1 | dyadic), data=df)
m.gs.ng <- lmer(global_synchrony ~ n_mutual_gaze + (1 | dyadic), data=df)
m.pl.ng <- lmer(abs_peak_lag ~ n_mutual_gaze + (1 | dyadic), data=df)
#
summary(m.gs.ng) # trend global synchrony
summary(m.ps.ng)
summary(m.pl.ng)
summary(m.lz.ng) # sig lag zero synchrony

tab_model(m.gs.ng, m.ps.ng, m.pl.ng, m.lz.ng, file="../results/model/bm_mutual_gaze.html")
```
```{r}
# sig
performance::icc(m.lz.ng)
m.lz.ng %>% anova()
#sjPlot::plot_model(m.lz.ng, type = "pred", terms = c("n_mutual_gaze"))
sjPlot::tab_model(m.lz.ng)
# trend 
performance::icc(m.gs.ng)
m.gs.ng %>% anova()
#sjPlot::plot_model(m.gs.ng, type = "pred", terms = c("n_mutual_gaze"))
sjPlot::tab_model(m.gs.ng)
```


```{r}
# Fit the model
m.lz.tg <- lmer(lag_zero ~ t_mutual_gaze + (1 | dyadic), data=df)
m.ps.tg <- lmer(peak_synchrony ~ t_mutual_gaze + (1 | dyadic), data=df)
m.gs.tg <- lmer(global_synchrony ~ t_mutual_gaze + (1 | dyadic), data=df)
m.pl.tg <- lmer(abs_peak_lag ~ t_mutual_gaze + (1 | dyadic), data=df)
#
summary(m.gs.tg)
summary(m.ps.tg ) 
summary(m.pl.tg)
summary(m.lz.tg) # sig
```

```{r}
# sig
performance::icc(m.lz.tg)
m.lz.tg %>% anova()
#sjPlot::plot_model(m.lz.tg, type = "pred", terms = c("t_mutual_gaze"))
sjPlot::tab_model(m.lz.tg)
```


```{r}
# Fit the model
m.lz.dg <- lmer(lag_zero ~ d_mutual_gaze + (1 | dyadic), data=df)
m.ps.dg <- lmer(peak_synchrony ~ d_mutual_gaze + (1 | dyadic), data=df)
m.gs.dg <- lmer(global_synchrony ~ d_mutual_gaze + (1 | dyadic), data=df)
m.pl.dg <- lmer(abs_peak_lag ~ d_mutual_gaze + (1 | dyadic), data=df)
#
summary(m.lz.dg) 
summary(m.ps.dg ) 
summary(m.gs.dg) 
summary(m.pl.dg)
```

### Global synchrony
#### Statistics
```{r}
# Summary statistics
df %>%
  group_by(condition) %>%
  get_summary_stats(global_synchrony, type = "common")

df %>%
  group_by(cq_level) %>%
  get_summary_stats(global_synchrony, type = "common")

# Basic plot
ggboxplot(df, x = "condition", y = "global_synchrony", add = "jitter", fill = "condition", xlab = "Video resolution", ylab = "Global synchrony level", outlier.shape = NA, width = 0.5, palette = "npg")

#pdf(file = "plots/gs_bm_box.pdf", width = 4, height = 4)
#ggboxplot(df, x = "condition", y = "global_synchrony", add = "jitter", fill = "condition", xlab = "Video resolution", ylab = "Global synchrony level", outlier.shape = NA, width = 0.5, palette = "npg")
#dev.off()
```

#### Mixed effect model
```{r}
# Fit the model
m.gs <- lmer(global_synchrony ~ condition*cq + (1 | dyadic), data=df)
summary(m.gs)
performance::icc(m.gs)
m.gs %>% anova()
sjPlot::plot_model(m.gs, type = "pred", terms = c("condition"))
sjPlot::tab_model(m.gs)
```
### Lag zero synchrony
#### Statistics
```{r}
# Summary statistics
df %>%
  group_by(condition) %>%
  get_summary_stats(lag_zero, type = "common")

df %>%
  group_by(cq_level) %>%
  get_summary_stats(lag_zero, type = "common")

# Box plot
#ggboxplot(df, x = "condition", y = "lag_zero", add = "jitter")
#ggboxplot(df, x = "cq_level", y = "lag_zero", add = "jitter")
```

#### Mixed effects model
```{r}
# Fit the model
m.lz <- lmer(lag_zero ~ condition + cq + (1 | dyadic), data=df)
summary(m.lz)
performance::icc(m.lz)
m.lz %>% anova()
#sjPlot::plot_model(m.lz, type = "pred", terms = c("cq", "condition"))
sjPlot::tab_model(m.lz)
```
### Peak synchrony
#### Statistics
```{r}
# Summary statistics
df %>%
  group_by(condition) %>%
  get_summary_stats(peak_synchrony, type = "common")

df %>%
  group_by(cq_level) %>%
  get_summary_stats(peak_synchrony, type = "common")

# Basic plot
pdf(file = "../results/plots/ps_bm_box.pdf",  
    width = 4, 
    height = 4)
ggboxplot(df, x = "condition", y = "peak_synchrony", add = "jitter", fill = "condition", xlab = "Video resolution", ylab = "Peak synchrony level", outlier.shape = NA, width = 0.5, palette = "npg")
dev.off()
```
#### Mixed effect model
```{r}
# Fit the model
m.ps <- lmer(peak_synchrony ~ condition + cq + (1 | dyadic), data=df)
summary(m.ps) # sig decreasing
performance::icc(m.ps)
m.ps %>% anova()
#sjPlot::plot_model(m.ps, type = "pred", terms = c("condition"))
sjPlot::tab_model(m.ps)
```
### Peak lag
#### Statistics
```{r}
# Summary statistics
df %>%
  group_by(condition) %>%
  get_summary_stats(abs_peak_lag, type = "common")

df %>%
  group_by(cq_level) %>%
  get_summary_stats(abs_peak_lag, type = "common")
```

#### Mixed effects model
```{r}
# Fit the model
m.pk <- lmer(abs_peak_lag ~ condition*cq + (1 | dyadic), data=df)
summary(m.pk)
#sjPlot::plot_model(m.pk, type = "pred", terms = c("cq", "condition"))
```
```{r}
tab_model(m.gs,m.lz, m.ps, m.pk, file="../results/model/m_bm.html")
```

## AU06
```{r}
df_au06 <- read_excel("../data/df_dyadic_au06.xlsx")
df_au06$condition <- factor(as.character(df_au06$condition), levels = c("240p", "480p", "1080p"))
df_au06$cq_level <- factor(as.character(df_au06$cq_level), levels = c("Bad", "Poor", "Fair", "Good", "Excellent"))
df_au06$dyadic <- factor(as.character(df_au06$dyadic))
df_au06$A_or_B <- factor(as.character(df_au06$A_or_B))
head(df_au06)
```

### The influence of mutual gaze
```{r}
# Fit the model
m.au06.lz.gn <- lmer(lag_zero ~ n_mutual_gaze + (1 | dyadic), data=df_au06)
m.au06.ps.gn <- lmer(peak_synchrony ~ n_mutual_gaze + (1 | dyadic), data=df_au06)
m.au06.gs.gn <- lmer(global_synchrony ~ n_mutual_gaze + (1 | dyadic), data=df_au06)
m.au06.pl.gn <- lmer(abs_peak_lag ~ n_mutual_gaze + (1 | dyadic), data=df_au06)
#
summary(m.au06.lz.gn) 
summary(m.au06.ps.gn) 
summary(m.au06.gs.gn) # trend
summary(m.au06.pl.gn) # trend

# Fit the model
m.au06.lz.gt <- lmer(lag_zero ~ t_mutual_gaze + (1 | dyadic), data=df_au06)
m.au06.ps.gt <- lmer(peak_synchrony ~ t_mutual_gaze + (1 | dyadic), data=df_au06)
m.au06.gs.gt <- lmer(global_synchrony ~ t_mutual_gaze + (1 | dyadic), data=df_au06)
m.au06.pl.gt <- lmer(abs_peak_lag ~ t_mutual_gaze + (1 | dyadic), data=df_au06)
#
summary(m.au06.lz.gt) # sig
summary(m.au06.ps.gt) # trend
summary(m.au06.gs.gt) 
summary(m.au06.pl.gt) # sig

# Fit the model
m.au06.lz.gd <- lmer(lag_zero ~ d_mutual_gaze + (1 | dyadic), data=df_au06)
m.au06.ps.gd <- lmer(peak_synchrony ~ d_mutual_gaze + (1 | dyadic), data=df_au06)
m.au06.gs.gd <- lmer(global_synchrony ~ d_mutual_gaze + (1 | dyadic), data=df_au06)
m.au06.pl.gd <- lmer(abs_peak_lag ~ d_mutual_gaze + (1 | dyadic), data=df_au06)
#
summary(m.au06.lz.gd) 
summary(m.au06.ps.gd) 
summary(m.au06.gs.gd) 
summary(m.au06.pl.gd) # trend
```
### Global synchrony
#### Statistics
```{r}
# Summary statistics
df_au06 %>%
  group_by(condition) %>%
  get_summary_stats(global_synchrony, type = "common")

df_au06 %>%
  group_by(cq_level) %>%
  get_summary_stats(global_synchrony, type = "common")

# Box plot
#ggboxplot(df_au06, x = "condition", y = "global_synchrony", add = "jitter")
#ggboxplot(df_au06, x = "cq_level", y = "global_synchrony", add = "jitter")
```
#### Mixed effect model
```{r}
# Fit the model
m.au06.gs <- lmer(global_synchrony ~ cq*condition + (1 | dyadic), data = df_au06)
summary(m.au06.gs)
performance::icc(m.au06.gs)
m.au06.gs %>% anova()
sjPlot::plot_model(m.au06.gs, type = "pred", terms = c("cq", "condition"))
sjPlot::tab_model(m.au06.gs)
```
### Lag zero synchrony
#### Statistics
```{r}
# Summary statistics
df_au06 %>%
  group_by(condition) %>%
  get_summary_stats(lag_zero, type = "common")

df_au06 %>%
  group_by(cq_level) %>%
  get_summary_stats(lag_zero, type = "common")
```
#### Mixed effect model
```{r}
# Fit the model
m.au06.lz <- lmer(lag_zero ~ cq*condition + (1 | dyadic), data = df_au06)
summary(m.au06.lz)
performance::icc(m.au06.lz)
m.au06.lz %>% anova()
#sjPlot::plot_model(m.au06.lz, type = "pred", terms = c("cq", "condition"))
sjPlot::tab_model(m.au06.lz)
```
### Peak synchrony
#### Statistics
```{r}
# Summary statistics
df_au06 %>%
  group_by(condition) %>%
  get_summary_stats(peak_synchrony, type = "common")

df_au06 %>%
  group_by(cq_level) %>%
  get_summary_stats(peak_synchrony, type = "common")
```
#### Mixed effect model
```{r}
# Fit the model
m.au06.ps <- lmer(peak_synchrony ~ cq*condition + (1 | dyadic), data = df_au06)
summary(m.au06.ps)
performance::icc(m.au06.ps)
m.au06.ps %>% anova()
#sjPlot::plot_model(m.au06.ps, type = "pred", terms = c("cq", "condition"))
sjPlot::tab_model(m.au06.ps)
```
### Peak lag
#### Statistics
```{r}
# Summary statistics
df_au06 %>%
  group_by(condition) %>%
  get_summary_stats(abs_peak_lag, type = "common")

df_au06 %>%
  group_by(cq_level) %>%
  get_summary_stats(abs_peak_lag, type = "common")
```
#### Mixed effect model
```{r}
# Fit the model
m.au06.pl <- lmer(abs_peak_lag ~ cq*condition + (1 | dyadic), data = df_au06)
summary(m.au06.pl) # sig cq decrease but in a good way near lag0
performance::icc(m.au06.pl)
m.au06.pl %>% anova()
sjPlot::plot_model(m.au06.pl, type = "pred", terms = c("cq", "condition"))
sjPlot::tab_model(m.au06.pl)
pdf(file = "../results/plots/m_pl_au06.pdf",   
    width = 6,
    height = 4) 
sjPlot::plot_model(m.au06.pl, type = "pred", colors = "social", terms = c("cq", "condition"), title = "") + labs(x = "Conversatinal Quality", y="Peak lag (s)")
dev.off()
```
## AU12
```{r}
df_au12 <- read_excel("../data/df_dyadic_au12.xlsx")
df_au12$condition <- factor(as.character(df_au12$condition), levels = c("480p", "240p",  "1080p"))
df_au12$cq_level <- factor(as.character(df_au12$cq_level), levels = c("Bad", "Poor", "Fair", "Good", "Excellent"))
df_au12$dyadic <- factor(as.character(df_au12$dyadic))
df_au12$A_or_B <- factor(as.character(df_au12$A_or_B))
head(df_au12)
```
### The influence of mutual gaze
```{r}
# Fit the model
m.au12.lz.gn <- lmer(lag_zero ~ n_mutual_gaze + (1 | dyadic), data=df_au12)
m.au12.ps.gn <- lmer(peak_synchrony ~ n_mutual_gaze + (1 | dyadic), data=df_au12)
m.au12.gs.gn <- lmer(global_synchrony ~ n_mutual_gaze + (1 | dyadic), data=df_au12)
m.au12.pl.gn <- lmer(abs_peak_lag ~ n_mutual_gaze + (1 | dyadic), data=df_au12)
#
summary(m.au12.lz.gn) 
summary(m.au12.ps.gn) 
summary(m.au12.gs.gn) 
summary(m.au12.pl.gn) 

# Fit the model
m.au12.lz.gt <- lmer(lag_zero ~ t_mutual_gaze + (1 | dyadic), data=df_au12)
m.au12.ps.gt <- lmer(peak_synchrony ~ t_mutual_gaze + (1 | dyadic), data=df_au12)
m.au12.gs.gt <- lmer(global_synchrony ~ t_mutual_gaze + (1 | dyadic), data=df_au12)
m.au12.pl.gt <- lmer(abs_peak_lag ~ t_mutual_gaze + (1 | dyadic), data=df_au12)
#
summary(m.au12.lz.gt) # sig
summary(m.au12.ps.gt) 
summary(m.au12.gs.gt) 
summary(m.au12.pl.gt) # sig

# Fit the model
m.au12.lz.gd <- lmer(lag_zero ~ d_mutual_gaze + (1 | dyadic), data=df_au12)
m.au12.ps.gd <- lmer(peak_synchrony ~ d_mutual_gaze + (1 | dyadic), data=df_au12)
m.au12.gs.gd <- lmer(global_synchrony ~ d_mutual_gaze + (1 | dyadic), data=df_au12)
m.au12.pl.gd <- lmer(abs_peak_lag ~ d_mutual_gaze + (1 | dyadic), data=df_au12)
#
summary(m.au12.lz.gd)
summary(m.au12.ps.gd) 
summary(m.au12.gs.gd) # trend
summary(m.au12.pl.gd) # sig
```
### Global synchrony
#### Statistics
```{r}
df_au12 %>%
  group_by(condition) %>%
  get_summary_stats(global_synchrony, type = "common")

df_au12 %>%
  group_by(cq_level) %>%
  get_summary_stats(global_synchrony, type = "common")
```
#### Mixed effect model
```{r}
# Fit the model
m.au12.gs <- lmer(global_synchrony ~ condition*cq + (1 | dyadic), data = df_au12)
summary(m.au12.gs) # sig for cq
performance::icc(m.au12.gs)
m.au12.gs %>% anova()
sjPlot::plot_model(m.au12.gs, type = "pred", terms = c("cq", "condition"))
sjPlot::tab_model(m.au12.gs)
pdf(file = "../results/plots/m_gs_au12.pdf",   
    width = 6,
    height = 4) 
sjPlot::plot_model(m.au12.gs, type = "pred", colors = "social", terms = c("cq", "condition"), title = "") + labs(x = "Conversatinal Quality", y="Global synchrony level")
dev.off()
```
### Lag zero synchrony
#### Statistics
```{r}
df_au12 %>%
  group_by(condition) %>%
  get_summary_stats(lag_zero, type = "common")

df_au12 %>%
  group_by(cq_level) %>%
  get_summary_stats(lag_zero, type = "common")
```
#### Mixed effect model
```{r}
# Fit the model
m.au12.lz <- lmer(lag_zero ~ condition + cq + (1 | dyadic), data = df_au12)
summary(m.au12.lz) 
performance::icc(m.au12.lz)
m.au12.lz %>% anova()
sjPlot::plot_model(m.au12.lz, type = "pred", terms = c("cq", "condition"))
sjPlot::tab_model(m.au12.lz)
```
### Peak synchrony
#### Statistics
```{r}
df_au12 %>%
  group_by(condition) %>%
  get_summary_stats(peak_synchrony, type = "common")

df_au12 %>%
  group_by(cq_level) %>%
  get_summary_stats(peak_synchrony, type = "common")
```
#### Mixed effect model
```{r}
# Fit the model
m.au12.ps <- lmer(peak_synchrony ~ condition*cq + (1 | dyadic), data = df_au12)
summary(m.au12.ps) 
performance::icc(m.au12.ps)
m.au12.ps %>% anova()
sjPlot::plot_model(m.au12.ps, type = "pred", terms = c("cq","condition"))
sjPlot::tab_model(m.au12.ps)
```
### Peak lag
#### Statistics
```{r}
df_au12 %>%
  group_by(condition) %>%
  get_summary_stats(abs_peak_lag, type = "common")

df_au12 %>%
  group_by(cq_level) %>%
  get_summary_stats(abs_peak_lag, type = "common")
```
#### Mixed effect model
```{r}
# Fit the model
m.au12.pl <- lmer(abs_peak_lag ~ condition*cq + (1 | dyadic), data = df_au12)
summary(m.au12.pl)
performance::icc(m.au12.pl)
m.au12.pl %>% anova()
sjPlot::plot_model(m.au12.pl, type = "pred", terms = c("cq", "condition"))
sjPlot::tab_model(m.au12.pl)
```

